Der Titel des Beitrags, der auch etwas länger sein und über zwei Zeilen reichen kann

### 2017-01-23 paper.tex
Refine README.md to include all three options, readd paper.tex, add lni-author-template.tex
Add minimum biblatex version requirement to \usepackage{biblatex} statement

%for easy quotations: \enquote{text}
%also required by biblatex
\usepackage{csquotes}
\usepackage[
  backend=biber, % UTF-8 support
  style=LNI,     % The GI style - see https://www.ctan.org/pkg/biblatex-lni
  natbib=true    % Requried for \Citet
]{biblatex}
\bibliography{paper}

@@

% If you change this to todonotes, keep in mind that it changes the positioning of the headings on pages 2 onwards.
% So, disable todonotes upon final submission.
% This does not happen when using fixmetodonotes, so this package is used.
% Documentation available at http://texdoc.net/texmf-dist/doc/latex/fixmetodonotes/README
\usepackage{fixmetodonotes}

>>>>

%for easy quotations: \enquote{text}
%also required by biblatex
\usepackage{csquotes}
\usepackage[
  backend=biber, % UTF-8 support
  style=LNI,     % The GI style - see https://www.ctan.org/pkg/biblatex-lni
  natbib=true    % Requried for \Citet
]{biblatex}[2016-09-15] %at least version 3.6 of biblatex is required.
\bibliography{paper}

@@

% Documentation available at http://texdoc.net/texmf-dist/doc/latex/fixmetodonotes/README
% Alternative packages: todonotes and pdfcomment
% This offers \TODO and \FIXME
\usepackage{fixmetodonotes}
